### 2018-06-03 doc/manuscript.Rmd
fixed final conclusion

In conclusion, we found that a TGFA composition indicative of higher DNL
(containing higher 14:0, 14:1n-7, 16:0, and 16:1n-7) associated strongly with lower
insulin sensitivity and (more moderately) with lower beta-cell function. The fatty
acids that clustered together represent fatty acids created from DNL, which is
characteristic of higher simple carbohydrate (e.g. added sugar) intake. Our
results, which are congruent with current evidence, suggest that higher DNL,
likely due to greater intake of simple or refined carbohydrates, may increase the
risk of T2D through worsening of insulin sensitivity.

>>>>

In conclusion, we found that a TGFA composition containing higher proportions of
14:0, 14:1n-7, 16:0, and 16:1n-7 associated strongly with lower insulin
sensitivity and (more moderately) with lower beta-cell function. We also found
that most other TGFA (e.g. 20:0, most omega 6 and 9 TGFA, and 20:5n-3)
associated positively with insulin sensitivity. Only a few TGFA associated
positively and consistently with beta-cell function (e.g. 18:1n-7, 20:2n-6). 
These results provide more insight into how individual TGFA contribute to the
pathogenesis of T2D while reinforcing the importance and value of clinically
measured total TG as a indicator of metabolic health.
